---
title: "CoinGeckoR"
output: github_document
---

### R wrapper for the CoinGecko API

*Package is currently under development and in its infancy*

https://www.coingecko.com/en/api

### How to install CoinGeckoR

---

GitHub
```{r, eval=FALSE}
library(devtools)
install_github("https://github.com/SamBuckberry/CoinGeckoR")
```

Load the library
```{r}
library(CoinGeckoR)
```

### Examples of CoinGeckoR functions

---

#### Simple  

---

`/simple/ping`
Ping the CoinGecko API
```{r}
ping_gecko()
```

`/simple/price`
Get the current price of any cryptocurrencies in any other supported currencies that you need.
```{r}

```

`/simple/supported_vs_currencies`
Get list of supported_vs_currencies  
```{r}
support_list <- supported_vs_currencies()
head(support_list)
```


#### Coins  

---

`/coins/list`
List all supported coins id, name and symbol.
```{r}

```


Retreive coin price history for a specific date
```{r}
btc_price_df <- get_coin_history(coin = "bitcoin",
                                   date_POSIXlt = as.POSIXlt("2015-12-31"))
head(btc_price_df)
```


