---
title: "CoinGeckoR"
output: github_document
---

### R functions for interacting with the CoinGecko API

*Package is currently under development and in its infancy*

CoinGecko API documentation (v3)
https://www.coingecko.com/api/documentations/v3

### Installation

---

GitHub
```{r, eval=FALSE}
library(devtools)
install_github("https://github.com/SamBuckberry/CoinGeckoR")
```

Load the library
```{r}
library(CoinGeckoR)
```

### CoinGeckoR functions

---

#### Ping

- `/simple/ping`  
Check API server status
```{r}
ping_gecko()
```


#### Simple  

---

- `/simple/price`  
Get the current price of any cryptocurrencies in any other supported currencies that you need.

```{r}
price(ids = "bitcoin", vs_currencies = "aud")
```

- `/simple/token_price/{id}`  
Get current price of tokens (using contract addresses) for a given platform in any other currency that you need.
```{r}

```

- `/simple/supported_vs_currencies`  
Get list of supported_vs_currencies  
```{r}
support_list <- supported_vs_currencies()
support_list[1:6]
```


#### Coins  

---

- `/coins/list`
List all supported coins id, name and symbol.
```{r}
cl <- coins_list()

# Make as a data.frame
cl <- do.call(rbind, cl)
cl[1:3, ]
```

- `/coins/markets`
List all supported coins price, market cap, volume, and market related data.
```{r}
mkt <- markets(vs_currency = "usd", ids = "bitcoin")

mkt[[1]][c("id", "current_price")]
```


#### Categories

- `/coins/categories/list`
List all categories
```{r}
cat_list <- coin_categories()

cat_list <- do.call(rbind, cat_list)
head(cat_list)
```


#### Examples
Retreive coin price history for a specific date
```{r}
btc_price_df <- get_coin_history(coin = "bitcoin",
                                   date_POSIXlt = as.POSIXlt("2015-12-31"))
head(btc_price_df)
```


